### 2022-07-27 manuscript.tex
Merge pull request #267 from SORTEE-Github-Hackathon/phpb-organisations [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/def3bc7be9dc165100774b0e53208fbd9e00a9ba.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/def3bc7be9dc165100774b0e53208fbd9e00a9ba/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2748183697

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/50a63631e17fef9d3b6a8798a25b2567c940fca3/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/50a63631e17fef9d3b6a8798a25b2567c940fca3}{SORTEE-Github-Hackathon/manuscript@50a6363}
on July 27, 2022.

@@

\hypertarget{github-organizations}{%
\subsubsection{GitHub Organizations}\label{github-organizations}}

GitHub Organizations are shared virtual spaces that allow teams to work in different repositories, while remaining tied together under a larger group, such as a laboratory, department, or project involving several teams.
Organizations are well-suited to ensure larger projects with many steps or moving parts are constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on any one individual.
Because the repositories are grouped, members can reference and contribute to each other's work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.

@@

As an example, GitHub Organizations are particularly well-suited to host documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other relevant documents that evolve collaboratively over time.
In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data are lost.
This application extends to research centres, which may include several distinct projects that remain linked to institutions {[}\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}){]}.
The team organizing the hackathon which inspired this article used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to centralize the project development, from meeting notes to, ultimately, this manuscript.
Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be continously updated by an ever-evolving group of contributors.

@@

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{About projects (beta). \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/trying-out-the-new-projects-experience/about-projects}.}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/def3bc7be9dc165100774b0e53208fbd9e00a9ba/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/def3bc7be9dc165100774b0e53208fbd9e00a9ba}{SORTEE-Github-Hackathon/manuscript@def3bc7}
on July 27, 2022.

@@

\hypertarget{organizing-and-managing-teams}{%
\subsubsection{Organizing and managing teams}\label{organizing-and-managing-teams}}

GitHub Organizations are shared virtual spaces that allow teams to work in different repositories, while remaining tied together under a larger group, such as a laboratory, department, or project involving several teams.
Organizations allow larger projects with many steps or moving parts to be constrained to one virtual space, where outputs and sub-projects can be easily accessed and located without relying on individuals.
Because the repositories are grouped, members can reference and contribute to each others work without necessarily being part of the same repository, broadening the accessibility and longevity of code and writing contributions.

@@

As an example, GitHub Organizations are particularly well-suited to host documents and projects within a laboratory, such as research compendia, codes of conduct, protocols, training documents, and other relevant documents that evolve collaboratively over time.
In this way, teams have full ownership of repositories within an organization, while ensuring that these materials stay accessible to the laboratory after people have moved on or when locally-stored data are lost.
This application extends to research centres, which may include several distinct projects that remain linked to institutions {[}\emph{e.g.}, the German Centre for Integrative Biodiversity Research (iDiv, \url{https://github.com/idiv-biodiversity}){]}.
The team organizing the hackathon which inspired this article used a GitHub Organization (SORTEE-Github-Hackathon, \url{https://github.com/SORTEE-Github-Hackathon}) to centralize the project development, from meeting notes to, ultimately, this manuscript.
Organizations are also convenient for hosting learning materials, including lectures or workshops, such as the Québec Centre for Biodiversity Science R Workshop Series (QCBSRworkshops, \url{https://github.com/QCBSRworkshops}) or the University of Edinburgh's Coding Club (Coding Club, \url{https://github.com/ourcodingclub}), which may be continuously updated by an ever-evolving group of contributors.

@@

\leavevmode\vadjust pre{\hypertarget{ref-RhBKe0MG}{}}%
\CSLLeftMargin{22. }
\CSLRightInline{About Projects. \emph{GitHub Docs} \url{https://ghdocs-prod.azurewebsites.net/en/issues/planning-and-tracking-with-projects/learning-about-projects/about-projects}.}
